### 2023-01-20 code/may.Rmd

df <- map_dfr(seq(0, 1, length.out = 31),
function(init) {
  df <- tibble(init, time = 1:50, x = init)
  for(t in 1:max(df$time)) {
    df[t+1,] = tibble(init, time = t+1, x = f(df$x[t], F)) 
  }
  df
})
df2 <- df |> mutate(h = F_MSY * x)
df2 |> ggplot(aes(time,x, col=init, group=init)) +
  geom_line() + ylim(0,1) + 
  geom_hline(aes(yintercept=X[i]))
```
```{r}

>>>>

df <- map_dfr(seq(0, 1, length.out = 31),
function(init) {
  df <- tibble(init, time = 1:50, x = init)
  for(t in 1:max(df$time)) {
    df[t+1,] = tibble(init, time = t+1, x = f(df$x[t], F_MSY)) 
  }
  df
})
df2 <- df |> mutate(h = F_MSY * x)
df2 |> ggplot(aes(time,x, col=init, group=init)) +
  geom_line() + ylim(0,1) + 
  geom_hline(aes(yintercept=X[i]))
```
```{r}
